Including EW and mixed QCD-EW corrections into PDF fits

### 2020-07-28 paper/sec-results.tex
Small tweaks

In this section we demonstrate the capabilities of \textsc{PineAPPL} by
computing fast interpolation grids, accurate to NLO QCD and NLO QCD+EW,
for a representative set of processes in which EW corrections are expected 
to be sizeable. In order to consider some realistic kinematics for these
processes, we resort to measurements commonly devised for inclusion in PDF
fits. Our aim is twofold. On the one hand, we want to validate the results
obtained with \textsc{PineAPPL}; on the other hand, we want to assess the
impact of the EW corrections for usual experimental setups. We describe first
the processes and measurements that we consider, then the computational
settings that we adopt, and finally the results that we obtain.

@@

The central values of the renormalisation and factorisation scales, $\mu_R$ and
$\mu_F$, are chosen, for each process, as follows. In the case of DY lepton pair
production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is the mass
of the $Z$-boson, for the ATLAS measurement, and the dynamic scale
$\mu_R=\mu_F=$ for the CMS measurement.
In the case of top-quark pair production, we use the dynamic scales
$\mu_R=\mu_F=\sqrt{m_t^2+(p_T^t)^2}{\Big /}2$ for the distribution differential
in the transverse momentum of the top quark, and $\mu_R=\mu_F=H_T/4$ for the
distribution differential in the invariant mass of the top-quark pair, where
$H_T=\sqrt{m_t^2+(p_T^t)^2}+\sqrt{m_t^2+(p_T^{\bar{t}})}$, with $m_t$,
$p_T^t$ and $p_T^{\bar t}$ the mass of the top quark and the transverse momenta
of the top and antitop quarks, respectively. These choices were demonstrated
to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
In the case of $Z$-boson production with non-zero transverse momentum, we use
$\mu_R=\mu_F=M_Z$. In order to estimate the missing higher-order uncertainty,
we allow the events to be reweighted in the Monte Carlo generation upon scale
variations. As is customary, the factorisation and renormalisation scales
are varied down to a factor $1/2$ and up to a factor $2$.

>>>>

In this section we demonstrate the capabilities of \textsc{PineAPPL} by
computing fast interpolation grids, accurate to NLO QCD and NLO QCD+EW,
for a representative set of processes in which EW corrections are expected 
to be sizeable. In order to consider some realistic kinematics for these
processes, we resort to measurements commonly devised for inclusion in PDF
fits. Our aim is twofold. First, we want to validate the results
obtained with \textsc{PineAPPL}; second, we want to assess the
impact of the EW corrections for usual experimental setups. We describe, first,
the processes and measurements that we consider, then the computational
settings that we adopt, and finally the results that we obtain.

@@

The central values of the renormalisation and factorisation scales, $\mu_R$ and
$\mu_F$, are chosen, for each process, as follows. In the case of DY lepton pair
production, we use the fixed scale $\mu_R=\mu_F=M_Z$, where $M_Z$ is the mass
of the $Z$-boson, for the ATLAS measurement, and the dynamic scale
$\mu_R=\mu_F=$ for the CMS measurement.
In the case of top-quark pair production, we use the dynamic scales
$\mu_R=\mu_F=\sqrt{m_t^2+(p_T^t)^2}{\Big /}2$ for the distribution differential
in the transverse momentum of the top quark, and $\mu_R=\mu_F=H_T/4$ for the
distribution differential in the invariant mass of the top-quark pair, where
$H_T=\sqrt{m_t^2+(p_T^t)^2}+\sqrt{m_t^2+(p_T^{\bar{t}})}$, with $m_t$,
$p_T^t$ and $p_T^{\bar t}$ the mass of the top quark and the transverse momenta
of the top and antitop quarks, respectively. These choices were demonstrated
to maximise the convergence of the perturbative expansion~\cite{Czakon:2016dgf}.
In the case of $Z$-boson production with non-zero transverse momentum, we use
$\mu_R=\mu_F=M_Z$. In order to estimate the missing higher-order uncertainty,
we allow the events to be reweighted in the Monte Carlo generation upon scale
variations. As is customary, the factorisation and renormalisation scales
are varied down to a factor $1/2$ and up to a factor $2$, and an envelope
from the nine-point scale variations is constructed.
